Music Recommendation System Using the Million Song Dataset

### 2015-05-08 writeup/MSDgroupwriteup.tex
table
Update MSDgroupwriteup.tex

\subsection{Data and Statistics}
The main source of data for this project was the Million Song Data Set (MSD)  \citep{Bertin-Mahieux2011}. We used the sample data set from the Kaggle competition which contains tuples of user id, song id, and play count.

The sample data set had $110000$ users, $163206$ songs, and the number of play counts for each user and song pair.
The scale of the data was too large to explore on our computers, so we subset the data down to a size easily handled by an average laptop.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{../plots/final/cumsum-songs.png} 
   \caption{ }
   \label{fig:t}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{../plots/final/cumsum-users.png} 
   \caption{ }
   \label{fig:t}
\end{figure}

@@

%\subsection{Naked Kmeans }
%\subsection{Non-Negative Matrix Factorization}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lc}

\hline
\bf{Algorithm} &  \bf{MAP score}\\ \hline
Item Based  CF  &  0.0479 \\ 
Artist Based Popularity Baseline  & 0.0448    \\ 
User Based  CF  &  0.0377 \\ 
Matrix Factorization  &   0.0143  \\ 
Top 500 Songs by Count  Baseline &  0.0138  \\ 
Top 500 Songs by Plays  Baseline &  0.0126  \\ 
\end{tabular}
\end{center}
\end{table}

@@

  \item Link to our github repository: \url{https://github.com/eringrand/musicanalysis}
  \item The MSD Kaggle challenge: \url{https://www.kaggle.com/c/msdchallenge}
  \item The user, song, play count dataset: \url{https://www.kaggle.com/c/msdchallenge/download/kaggle_visible_evaluation_triplets.zip}

>>>>

\subsection{Data and Statistics}
The main source of data for this project was the Million Song Data Set (MSD)  \citep{Bertin-Mahieux2011}. We used the sample data set from the Kaggle competition which contains tuples of user id, song id, and play count. We also used data which links songs to artists through track ids. The links to these datasets can be found in the Appendix.

The sample data set had $110000$ users, $163206$ songs, and the number of play counts for each user and song pair. The statistics are summarized below:

\begin{table}[h]
\begin{center}
\begin{tabular}{lcc}
\hline
Measurement & Plays Across Songs & Plays Across Users \\
\hline
Count &  163206 & 110000 \\
Mean  &     8.890194 & 13.190300  \\
Std      &    46.780258 & 8.070827 \\
Min      &    1.0  & 5.0  \\
Max     &   5043 &  53 \\
\end{tabular}
\end{center}
\end{table}

The scale of the data was too large to explore on our computers, so we subset the data down to a size easily handled by an average laptop.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{../plots/final/cumsum-songs.png} 
   \caption{Percentage of users accounted for versus songs with increasing number of plays.}
   \label{fig:t}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=4in]{../plots/final/cumsum-users.png} 
   \caption{Percentage of songs accounted for versus users with increasing number of plays.}
   \label{fig:t}
\end{figure}

@@

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lc}
\hline
\bf{Algorithm} &  \bf{MAP score}\\ \hline
Item Based  CF  &  0.0479 \\ 
Artist Based Popularity Baseline  & 0.0448    \\ 
User Based  CF  &  0.0377 \\ 
Matrix Factorization  &   0.0143  \\ 
Top 500 Songs by Count  Baseline &  0.0138  \\ 
Top 500 Songs by Plays  Baseline &  0.0126  \\ 
\end{tabular}
\end{center}
\end{table}

@@

  \item Link to our github repository: \url{https://github.com/eringrand/musicanalysis}
  \item The MSD Kaggle challenge: \url{https://www.kaggle.com/c/msdchallenge}
  \item The user, song, play count dataset: \url{https://www.kaggle.com/c/msdchallenge/download/kaggle_visible_evaluation_triplets.zip}
  \item Data to link songs to artists through track ids: \url{http://labrosa.ee.columbia.edu/millionsong/sites/default/files/AdditionalFiles/track_metadata.db}
